I began by listing Canada's national television broadcasters, Canada's top 20 English-language newspapers by circulation (excluding ``commuter'' arts papers; circulation data obtained from Newspapers Canada 2013 audited circulation figures), and then adding the largest newspaper for each of the remaining provinces not represented in the initial dataset. The database searched was LexisNexis Academic.

The search terms were (\textit{Member Name} AND (MP OR Member of Parliament)). LexisNexis prohibits search automation or large-scale data scraping. Of n=1,849 MPs post-1993 federal election, results were available for n=1,810. From visual inspection, the remaining MPs typically represented overwhelmingly French districts in Qu\'{e}bec. Canadian press sources tend to be unilingual, so press coverage of these MPs may only be available in French-language media that are not captured by this dataset.

The below source table is sorted by circulation or viewership size descending within each category:

\setstretch{1}
\begin{longtable}{l l l r l}
\textbf{Source} & \textbf{Location} & \textbf{Start Date} & \textbf{Notes} \\
\hline
\textbf{Newscasts} & & & \\
CBC News & National & Aug. 2006 & \\
CTV News & National & N.A. & Not available \\
Global News & National & N.A. & Not available \\
\hline
\textbf{Top 20 Newspapers} & & \\
Toronto Star & Toronto, ON & Sept. 1985 & \\
Globe and Mail & National & Nov. 1977 & \\
Toronto Sun & Toronto, ON & Mar. 2016 & Not available \\
National Post & National & Jan. 1985 & \\
Vancouver Sun & Vancouver, BC & Jul. 1991 & \\
Province & Vancouver, BC & Jan. 2000 & \\
Calgary Herald & Calgary, AB & Jul. 1991 & \\
Winnipeg Free Press & Winnipeg, MB & N.A. & Not available \\
Ottawa Citizen & Ottawa, ON & Jul. 1991 & \\
Montreal Gazette & Montreal, QC & Apr. 1985 & \\
Hamilton Spectator & Hamilton, ON & Oct. 1991 & \\
Edmonton Journal & Edmonton, AB & Jan. 2000 & \\
Chronicle-Herald & Halifax, NS & N.A. & Not available \\
London Free Press & London, ON & Mar. 2016 & Not applicable \\
Calgary Sun & Calgary, AB & Mar. 2016 & Not applicable \\
Winnipeg Sun & Winnipeg, MB & Mar. 2016 & Not applicable \\
Waterloo Region Record & Waterloo, ON & N.A. & Not available \\
Windsor Star & Windsor, ON & Jan. 2000 & \\
Times Colonist & Victoria, BC & Jan. 2000 & \\
Edmonton Sun & Edmonton, AB & Mar. 2016 & Not applicable \\
\hline 
\textbf{Remaining Provinces} & & \\
Star-Phoenix & Saskatoon, SK & Jan. 2000 & \\
Telegram & St. John's, NL & Jan. 2000 & \\
Guardian & Charlottetown, PE & Jan. 2000 & \\
Times \& Transcript & Moncton, NB & Jan. 1998 & \\
\hline 
\end{longtable}
\setstretch{2}